### 2012-10-30 paper_sean/results.tex

\figOneOnTwo[h!]{threeplots}{FINAL_kyrre_sean_fitness}{0.62}{servo_plot_111}{.48}{frequencyPlotThreshFinal}{.48}
{HyperNEAT outperforms a genetic algorithm with a simpler encoding, when both algorithms are combined with a simulator. Plotted are means over 20 runs in simulation (solid lines) $\pm$ STD (dashed lines). HyperNEAT gaits are 54.3\% faster in
simulation and 5.4\% faster in reality~(\tabref{results}).
\textbf{Left: }
Servo positions over time (for nine servos) for a simulated HyperNEAT gait. HyperNEAT produces gaits that are smooth, symmetrical, and contain other regularities. 
\textbf{Right: }Mean gait frequency averaged over 20 runs. 
Gaits with frequencies above a threshold (horizontal line) receive a fitness penalty. HyperNEAT quickly learns to produce gaits with frequencies low enough to avoid this penalty.
}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
                                         &              & Simulated  & Real Vel. & Real Vel.  \\
                                         & Evaluations  & Velocity &    (CCML)     & (ROBIN) \\
\hline
Parameterized gaits + optimization \cite{yos:clune}   &153    & --    & 5.8 & --\\
\hline
HyperNEAT in hardware \cite{yos:clune}                 & 180         & --         &   9.7  & --   \\
\hline
RL PoWER Spline \cite{haocheng}                         & 300         & --         &   11.1 & --\\
\hline
GA + simulator \cite{glette}             & 60000       & *16.7       &   13.8   & \textbf{17.8}  \\
\hline
HyperNEAT + simulator [this paper]                     & 40000       & \textbf{25.4}       &   \textbf{14.5} & --\\
\hline
\end{tabular}
\caption{Velocities of learned gaits in simulation and on two different copies of the QuadraTot robot. Subject to availability, data are reported from the experiments for this paper and three previous studies. Reported are the total number of evaluations per run, the average of the fastest gaits produced in each run in simulation, and the fastest gait produced on two different copies of the QuadraTot robot (CCML and ROBIN, see text). *Instead of using the single fitness value reported in~\cite{glette}, we ran 19 additional runs and used the average fitness of those 20 runs. Velocities are in cm/s, and bold indicates the best performance.}  
\tablabel{results}
\end{center}
\end{table}

>>>>

\figOneOnTwo[h!]{threeplots}{FINAL_sean_kyrre_fitness}{0.62}{servo_plot_111}{.48}{frequencyPlotThreshFinal}{.48}
{HyperNEAT outperforms a genetic algorithm with a simpler encoding, when both algorithms are combined with a simulator. Plotted are means over 20 runs in simulation (solid lines) $\pm$ STD (dashed lines). HyperNEAT gaits are 54.3\% faster in
simulation and 5.4\% faster in reality~(\tabref{results}).
\textbf{Left: }
Servo positions over time (for nine servos) for a simulated HyperNEAT gait. HyperNEAT produces gaits that are smooth, symmetrical, and contain other regularities. 
\textbf{Right: }Mean gait frequency averaged over 20 runs. 
Gaits with frequencies above a threshold (horizontal line) receive a fitness penalty. HyperNEAT quickly learns to produce gaits with frequencies low enough to avoid this penalty.
}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
                                         &              & Simulated  & Real Vel. & Real Vel.  \\
                                         & Evaluations  & Velocity &    (CCML)     & (ROBIN) \\
\hline
Parameterized gaits + optimization \cite{yos:clune}   &153    & --    & 5.8 & --\\
\hline
HyperNEAT in hardware \cite{yos:clune}                 & 180         & --         &   9.7  & --   \\
\hline
RL PoWER Spline \cite{haocheng}                         & 300         & --         &   11.1 & --\\
\hline
GA + simulator \cite{glette}             & 60000       & *16.7       &   13.8   & \textbf{17.8}  \\
\hline
HyperNEAT + simulator [this paper]                     & 40000       & \textbf{25.4}       &   \textbf{14.5} & --\\
\hline
\end{tabular}
\vspace{.35cm}
\caption{Velocities of learned gaits in simulation and on two different copies of the QuadraTot robot. Subject to availability, data are reported from the experiments for this paper and three previous studies. Reported are the total number of evaluations per run, the average of the fastest gaits produced in each run in simulation, and the fastest gait produced on two different copies of the QuadraTot robot (CCML and ROBIN, see text). *Instead of using the single fitness value reported in~\cite{glette}, we ran 19 additional runs and used the average fitness of those 20 runs. Velocities are in cm/s, and bold indicates the best performance.}  
\tablabel{results}
\end{center}
\end{table}
